---
title: "Long Term Logger DateTime Cleanup"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

 - Convert the DO logger Date_Time data into a date-time format
 - Combine the level logger Date and Time columns into one Date_Time column and convert into date-time format
 - Cleanup of USGS Skagit/Sauk mainstem data with column header name adjustment and date-time formatting (this only has to be done once)

Clear the workspace and close all graphic devices (two right panels in RStudio).  Bring in necessary packages.

```{r}
rm(list = ls())
graphics.off()
library(tidyverse)
library(lubridate)
```

Check the working directory and change if needed.

```{r}
getwd()
```


DO LOGGER DATE-TIME FORMATTING

Read in the .csv with DO logger data for each site.

```{r}
AA_DO_Logger <- read_csv("..\\..\\Data\\Raw Data\\DO Logger Data\\DO_Logger_Data_AA_James_Brown_READONLY.csv")
```

Check the data type for each column.  Date-Time is currently assigned as a character (chr) and DO is currently assigned as a "double class" (dbl) which are numeric values with decimal points.  There are also no seconds in the Date_Time column.

```{r}
AA_DO_Logger %>%
  head()
```

Parse the Date_Time column (identify and convert into POSIXct format which is readable by R) using the lubridate package in tidyverse.  When parsing date-time data you must specify the format that the data is currently in.  In this case, it is mdy_hm (there is no seconds data).

```{r}
AA_DO_Logger$Date_Time <- AA_DO_Logger$Date_Time %>%
  mdy_hm()
```

Export AA_DO_Logger as a .csv in the Derived Data folder in GitHub.  Using # so don't export a new .csv every time the code is run.  Just delete the # when you want to export.

```{r}
# AA_DO_Logger %>%
  # write_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\DO Data\\AA_DO_Logger_DateTime.csv")
```

Repeat for DO data at all sites.

AAE (Utopia)

```{r}
AAE_DO_Logger <- read_csv("..\\..\\Data\\Raw Data\\DO Logger Data\\DO_Logger_Data_AAE_Utopia_READONLY.csv")
AAE_DO_Logger$Date_Time <- AAE_DO_Logger$Date_Time %>%
  mdy_hm()
# AAE_DO_Logger %>%
  # write_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\DO Data\\AAE_DO_Logger_DateTime.csv")
```

AC (HMSP Slough)

```{r}
AC_DO_Logger <- read_csv("..\\..\\Data\\Raw Data\\DO Logger Data\\DO_Logger_Data_AC_HMSP_Slough_READONLY.csv")
AC_DO_Logger$Date_Time <- AC_DO_Logger$Date_Time %>%
  mdy_hm()
# AC_DO_Logger %>%
  # write_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\DO Data\\AC_DO_Logger_DateTime.csv")
```

AH (Martin Slough)

```{r}
AH_DO_Logger <- read_csv("..\\..\\Data\\Raw Data\\DO Logger Data\\DO_Logger_Data_AH_Martin_Slough_READONLY.csv")
AH_DO_Logger$Date_Time <- AH_DO_Logger$Date_Time %>%
  mdy_hm()
# AH_DO_Logger %>%
  # write_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\DO Data\\AH_DO_Logger_DateTime.csv")
```

AQ (Floral Lane)

```{r}
AQ_DO_Logger <- read_csv("..\\..\\Data\\Raw Data\\DO Logger Data\\DO_Logger_Data_AQ_Floral_Lane_READONLY.csv")
AQ_DO_Logger$Date_Time <- AQ_DO_Logger$Date_Time %>%
  mdy_hm()
# AQ_DO_Logger %>%
  # write_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\DO Data\\AQ_DO_Logger_DateTime.csv")
```

P (Savage Slough)

```{r}
P_DO_Logger <- read_csv("..\\..\\Data\\Raw Data\\DO Logger Data\\DO_Logger_Data_P_Savage_Slough_READONLY.csv")
P_DO_Logger$Date_Time <- P_DO_Logger$Date_Time %>%
  mdy_hm()
# P_DO_Logger %>%
  # write_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\DO Data\\P_DO_Logger_DateTime.csv")
```

Z (Site Z)

```{r}
Z_DO_Logger <- read_csv("..\\..\\Data\\Raw Data\\DO Logger Data\\DO_Logger_Data_Z_Off-channel_LBK_Skagit_READONLY.csv")
Z_DO_Logger$Date_Time <- Z_DO_Logger$Date_Time %>%
  mdy_hm()
# Z_DO_Logger %>%
  # write_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\DO Data\\Z_DO_Logger_DateTime.csv")
```



LEVEL LOGGER DATE_TIME FORMATTING

Read in the .csv with level logger (and temperature) data for each site.

```{r}
AA_Level_Logger <- read_csv("..\\..\\Data\\Raw Data\\Level Logger Data\\Level_Logger_Data_AA_James_Brown_READONLY.csv")
```

Now unite the Date and Time columns into one string.

```{r}
AA_Level_Logger <- AA_Level_Logger %>%
  unite(Date_Time, Date, Time, sep = " ")
```

Parse the Date_Time column (identify and convert into POSIXct format which is readable by R) using the lubridate package in tidyverse.  When parsing date-time data you must specify the format that the data is currently in.  In this case, it is mdy_hms.

```{r}
AA_Level_Logger$Date_Time <- AA_Level_Logger$Date_Time %>%
  mdy_hms()
```

Export AA_Level_Logger as a .csv in the Derived Data folder in GitHub.  Using # so don't export a new .csv every time the code is run.  Just delete the # when you want to export.

```{r}
# AA_Level_Logger %>%
  # write_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\Level Logger Data\\AA_Level_Logger_DateTime.csv")
```

Repeat for Level/Temp data at all sites.

AAB (RBK Sauk)

```{r}
AAB_Level_Logger <- read_csv("..\\..\\Data\\Raw Data\\Level Logger Data\\Level_Logger_Data_AAB_RBK_Sauk_READONLY.csv")
AAB_Level_Logger <- AAB_Level_Logger %>%
  unite(Date_Time, Date, Time, sep = " ")
AAB_Level_Logger$Date_Time <- AAB_Level_Logger$Date_Time %>%
  mdy_hms()
# AAB_Level_Logger %>%
  # write_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\Level Logger Data\\AAB_Level_Logger_DateTime.csv")
```

AAC (Sauk Boat Launch)

```{r}
AAC_Level_Logger <- read_csv("..\\..\\Data\\Raw Data\\Level Logger Data\\Level_Logger_Data_AAC_Sauk_Boat_Launch_READONLY.csv")
AAC_Level_Logger <- AAC_Level_Logger %>%
  unite(Date_Time, Date, Time, sep = " ")
AAC_Level_Logger$Date_Time <- AAC_Level_Logger$Date_Time %>%
  mdy_hms()
# AAC_Level_Logger %>%
  # write_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\Level Logger Data\\AAC_Level_Logger_DateTime.csv")
```

AAE (Utopia)

```{r}
AAE_Level_Logger <- read_csv("..\\..\\Data\\Raw Data\\Level Logger Data\\Level_Logger_Data_AAE_Utopia_READONLY.csv")
AAE_Level_Logger <- AAE_Level_Logger %>%
  unite(Date_Time, Date, Time, sep = " ")
AAE_Level_Logger$Date_Time <- AAE_Level_Logger$Date_Time %>%
  mdy_hms()
# AAE_Level_Logger %>%
  # write_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\Level Logger Data\\AAE_Level_Logger_DateTime.csv")
```

AAF (Illabot Chum Channel)

```{r}
AAF_Level_Logger <- read_csv("..\\..\\Data\\Raw Data\\Level Logger Data\\Level_Logger_Data_AAF_Illabot_Channel_READONLY.csv")
AAF_Level_Logger <- AAF_Level_Logger %>%
  unite(Date_Time, Date, Time, sep = " ")
AAF_Level_Logger$Date_Time <- AAF_Level_Logger$Date_Time %>%
  mdy_hms()
# AAF_Level_Logger %>%
  # write_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\Level Logger Data\\AAF_Level_Logger_DateTime.csv")
```

AB (McCleod Slough)

This dataset has one strange row with level and temperature values that aren't correct so that row is sliced out.

```{r}
AB_Level_Logger <- read_csv("..\\..\\Data\\Raw Data\\Level Logger Data\\Level_Logger_Data_AB_McCleod_Slough_READONLY.csv")
AB_Level_Logger <- AB_Level_Logger %>%
  unite(Date_Time, Date, Time, sep = " ")
AB_Level_Logger$Date_Time <- AB_Level_Logger$Date_Time %>%
  mdy_hms()
AB_Level_Logger <- AB_Level_Logger %>%
  slice(1:2650, 2652:12530)
# AB_Level_Logger %>%
  # write_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\Level Logger Data\\AB_Level_Logger_DateTime.csv")
```

AC (HMSP Slough)

```{r}
AC_Level_Logger <- read_csv("..\\..\\Data\\Raw Data\\Level Logger Data\\Level_Logger_Data_AC_HMSP_Slough_READONLY.csv")
AC_Level_Logger <- AC_Level_Logger %>%
  unite(Date_Time, Date, Time, sep = " ")
AC_Level_Logger$Date_Time <- AC_Level_Logger$Date_Time %>%
  mdy_hms()
# AC_Level_Logger %>%
  # write_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\Level Logger Data\\AC_Level_Logger_DateTime.csv")
```

AH (Martin Slough)

```{r}
AH_Level_Logger <- read_csv("..\\..\\Data\\Raw Data\\Level Logger Data\\Level_Logger_Data_AH_Martin_Slough_READONLY.csv")
AH_Level_Logger <- AH_Level_Logger %>%
  unite(Date_Time, Date, Time, sep = " ")
AH_Level_Logger$Date_Time <- AH_Level_Logger$Date_Time %>%
  mdy_hms()
# AH_Level_Logger %>%
  # write_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\Level Logger Data\\AH_Level_Logger_DateTime.csv")
```

AK (False Lucas Slough)

This dataset has one strange row with level and temperature values that aren't correct so that row is sliced out.

```{r}
AK_Level_Logger <- read_csv("..\\..\\Data\\Raw Data\\Level Logger Data\\Level_Logger_Data_AK_False_Lucas_Slough_READONLY.csv")
AK_Level_Logger <- AK_Level_Logger %>%
  unite(Date_Time, Date, Time, sep = " ")
AK_Level_Logger$Date_Time <- AK_Level_Logger$Date_Time %>%
  mdy_hms()
AK_Level_Logger <- AK_Level_Logger %>%
  slice(1:4085, 4087:14167)
# AK_Level_Logger %>%
  # write_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\Level Logger Data\\AK_Level_Logger_DateTime.csv")
```

AP (Powerline Pond)

```{r}
AP_Level_Logger <- read_csv("..\\..\\Data\\Raw Data\\Level Logger Data\\Level_Logger_Data_AP_Powerline_Pond_READONLY.csv")
AP_Level_Logger <- AP_Level_Logger %>%
  unite(Date_Time, Date, Time, sep = " ")
AP_Level_Logger$Date_Time <- AP_Level_Logger$Date_Time %>%
  mdy_hms()
# AP_Level_Logger %>%
  # write_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\Level Logger Data\\AP_Level_Logger_DateTime.csv")
```

AQ (Floral Lane)

```{r}
AQ_Level_Logger <- read_csv("..\\..\\Data\\Raw Data\\Level Logger Data\\Level_Logger_Data_AQ_Floral_Lane_READONLY.csv")
AQ_Level_Logger <- AQ_Level_Logger %>%
  unite(Date_Time, Date, Time, sep = " ")
AQ_Level_Logger$Date_Time <- AQ_Level_Logger$Date_Time %>%
  mdy_hms()
# AQ_Level_Logger %>%
  # write_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\Level Logger Data\\AQ_Level_Logger_DateTime.csv")
```

C (Deadman/Skiyou Slough)

```{r}
C_Level_Logger <- read_csv("..\\..\\Data\\Raw Data\\Level Logger Data\\Level_Logger_Data_C_Deadman_Skiyou_Slough_READONLY.csv")
C_Level_Logger <- C_Level_Logger %>%
  unite(Date_Time, Date, Time, sep = " ")
C_Level_Logger$Date_Time <- C_Level_Logger$Date_Time %>%
  mdy_hms()
# C_Level_Logger %>%
  # write_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\Level Logger Data\\C_Level_Logger_DateTime.csv")
```

D (West of Stevens)

```{r}
D_Level_Logger <- read_csv("..\\..\\Data\\Raw Data\\Level Logger Data\\Level_Logger_Data_D_West_Stevens_READONLY.csv")
D_Level_Logger <- D_Level_Logger %>%
  unite(Date_Time, Date, Time, sep = " ")
D_Level_Logger$Date_Time <- D_Level_Logger$Date_Time %>%
  mdy_hms()
# D_Level_Logger %>%
  # write_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\Level Logger Data\\D_Level_Logger_DateTime.csv")
```

K (Minkler Lake)

```{r}
K_Level_Logger <- read_csv("..\\..\\Data\\Raw Data\\Level Logger Data\\Level_Logger_Data_K_Minkler_Lake_READONLY.csv")
K_Level_Logger <- K_Level_Logger %>%
  unite(Date_Time, Date, Time, sep = " ")
K_Level_Logger$Date_Time <- K_Level_Logger$Date_Time %>%
  mdy_hms()
# K_Level_Logger %>%
  # write_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\Level Logger Data\\K_Level_Logger_DateTime.csv")
```

L (Cumberland Oxbow)

```{r}
L_Level_Logger <- read_csv("..\\..\\Data\\Raw Data\\Level Logger Data\\Level_Logger_Data_L_Cumberland_Oxbow_READONLY.csv")
L_Level_Logger <- L_Level_Logger %>%
  unite(Date_Time, Date, Time, sep = " ")
L_Level_Logger$Date_Time <- L_Level_Logger$Date_Time %>%
  mdy_hms()
# L_Level_Logger %>%
  # write_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\Level Logger Data\\L_Level_Logger_DateTime.csv")
```

P (Savage Slough)

```{r}
P_Level_Logger <- read_csv("..\\..\\Data\\Raw Data\\Level Logger Data\\Level_Logger_Data_P_Savage_Slough_READONLY.csv")
P_Level_Logger <- P_Level_Logger %>%
  unite(Date_Time, Date, Time, sep = " ")
P_Level_Logger$Date_Time <- P_Level_Logger$Date_Time %>%
  mdy_hms()
# P_Level_Logger %>%
  # write_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\Level Logger Data\\P_Level_Logger_DateTime.csv")
```

R (Hurn Field)

```{r}
R_Level_Logger <- read_csv("..\\..\\Data\\Raw Data\\Level Logger Data\\Level_Logger_Data_R_Hurn_Field_READONLY.csv")
R_Level_Logger <- R_Level_Logger %>%
  unite(Date_Time, Date, Time, sep = " ")
R_Level_Logger$Date_Time <- R_Level_Logger$Date_Time %>%
  mdy_hms()
# R_Level_Logger %>%
  # write_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\Level Logger Data\\R_Level_Logger_DateTime.csv")
```

Y (Thunderbird Slough)

```{r}
Y_Level_Logger <- read_csv("..\\..\\Data\\Raw Data\\Level Logger Data\\Level_Logger_Data_Y_Thunderbird_Slough_READONLY.csv")
Y_Level_Logger <- Y_Level_Logger %>%
  unite(Date_Time, Date, Time, sep = " ")
Y_Level_Logger$Date_Time <- Y_Level_Logger$Date_Time %>%
  mdy_hms()
# Y_Level_Logger %>%
  # write_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\Level Logger Data\\Y_Level_Logger_DateTime.csv")
```

Z (Site Z)

This dataset has one strange row with level and temperature values that aren't correct so that row is sliced out.

```{r}
Z_Level_Logger <- read_csv("..\\..\\Data\\Raw Data\\Level Logger Data\\Level_Logger_Data_Z_Off-channel_LBK_Skagit.csv")
Z_Level_Logger <- Z_Level_Logger %>%
  unite(Date_Time, Date, Time, sep = " ")
Z_Level_Logger$Date_Time <- Z_Level_Logger$Date_Time %>%
  mdy_hms()
Z_Level_Logger <- Z_Level_Logger %>%
  slice(1:2653, 2655:12535)
# Z_Level_Logger %>%
  # write_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\Level Logger Data\\Z_Level_Logger_DateTime.csv")
```

In hindsight it would've been easier to just make a function...next time.


USGS DATA CLEANUP

Download the USGS Skagit mainstem (Marblemount) data by following instructions in this link (https://serc.carleton.edu/hydromodules/steps/dm1.html).  Open the .txt file and manually delete the top rows that contain metadata.  Read in the .txt file.

```{r}
Skagit_Mainstem <- read_tsv("..\\..\\Data\\Raw Data\\USGS Mainstem Data\\Skagit_Mainstem_Gage_2021.txt")
```

Rename the column "datetime" to "Date_Time" and "151374_00060" to "Discharge_cfs" and then parse the Date-Time column.

```{r}
Skagit_Mainstem <- Skagit_Mainstem %>%
  rename("Date_Time" = "datetime", "Discharge_cfs" = "151374_00060")

Skagit_Mainstem$Date_Time <- Skagit_Mainstem$Date_Time %>%
  ymd_hm()
```
The top row failed to parse, so go ahead and delete that row.

```{r}
Skagit_Mainstem <- Skagit_Mainstem %>%
  slice(2:48067)
```

Export as a .csv to Derived Data folder in GitHub.

```{r}
# Skagit_Mainstem %>%
  # write_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\USGS Mainstem Data\\Skagit_Mainstem_Gage_2021.csv")
```

Repeat with the USGS Sauk mainstem (Darrington) data.

```{r}
Sauk_Mainstem <- read_tsv("..\\..\\Data\\Raw Data\\USGS Mainstem Data\\Sauk_Mainstem_Gage_2021.txt")

Sauk_Mainstem <- Sauk_Mainstem %>%
  rename("Date_Time" = "datetime", "Discharge_cfs" = "151420_00060")

Sauk_Mainstem$Date_Time <- Sauk_Mainstem$Date_Time %>%
  ymd_hm()

Sauk_Mainstem <- Sauk_Mainstem %>%
  slice(2:20545)

# Sauk_Mainstem %>%
  # write_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\USGS Mainstem Data\\Sauk_Mainstem_Gage_2021.csv")
```


