---
title: "Long Term Logger DateTime Cleanup"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

 - Convert the DO logger Date_Time data into a date-time format
 - Combine the level logger Date and Time columns into one Date_Time column and convert into date-time format

Clear the workspace and close all graphic devices (two right panels in RStudio).  Bring in necessary packages.

```{r}
rm(list = ls())
graphics.off()
library(tidyverse)
library(lubridate)
```

Check the working directory and change if needed.

```{r}
getwd()
```


DO LOGGER DATE-TIME FORMATTING

Read in the .csv with DO logger data for each site.

```{r}
AA_DO_Logger <- read_csv("..\\..\\Data\\Raw Data\\DO Logger Data\\DO_Logger_Data_AA_James_Brown_READONLY.csv")
```

Check the data type for each column.  Date-Time is currently assigned as a character (chr) and DO is currently assigned as a "double class" (dbl) which are numeric values with decimal points.

```{r}
AA_DO_Logger %>%
  head()
```


