---
title: "Long Term Logger DateTime Cleanup"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

 - Convert the DO logger Date_Time data into a date-time format
 - Combine the level logger Date and Time columns into one Date_Time column and convert into date-time format

Clear the workspace and close all graphic devices (two right panels in RStudio).  Bring in necessary packages.

```{r}
rm(list = ls())
graphics.off()
library(tidyverse)
library(lubridate)
```

Check the working directory and change if needed.

```{r}
getwd()
```


DO LOGGER DATE-TIME FORMATTING

Read in the .csv with DO logger data for each site.

```{r}
AA_DO_Logger <- read_csv("..\\..\\Data\\Raw Data\\DO Logger Data\\DO_Logger_Data_AA_James_Brown_READONLY.csv")
```

Check the data type for each column.  Date-Time is currently assigned as a character (chr) and DO is currently assigned as a "double class" (dbl) which are numeric values with decimal points.  There are also no seconds in the Date_Time column.

```{r}
AA_DO_Logger %>%
  head()
```

Parse the Date_Time column (identify and convert into POSIXct format which is readable by R) using the lubridate package in tidyverse.  When parsing date-time data you must specify the format that the data is currently in.  In this case, it is mdy_hm (there is no seconds data).

```{r}
AA_DO_Logger$Date_Time <- AA_DO_Logger$Date_Time %>%
  mdy_hm()
```

Export AA_DO_Logger as a .csv in the Derived Data folder in GitHub.  Using # so don't export a new .csv every time the code is run.  Just delete the # when you want to export.

```{r}
#AA_DO_Logger %>%
  #write_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\AA_DO_Logger_DateTime.csv")
```


LEVEL LOGGER DATE_TIME FORMATTING

Read in the .csv with level logger (and temperature) data for each site.

```{r}
AA_Level_Logger <- read_csv("..\\..\\Data\\Raw Data\\Level Logger Data\\Level_Logger_Data_AA_James_Brown_READONLY.csv")
```

Now unite the Date and Time columns into one string.

```{r}
AA_Level_Logger <- AA_Level_Logger %>%
  unite()
```

