---
title: "DO Time Series Plots"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

 - Create temperature time series plots for sites that only had temperature logger and no level logger.
 - Create DO time series plots from long term logger data.  Since these were placed for such a short amount of time at each site, it would be more informative for them to be their own plot to see diel changes in DO.

Clear the workspace and close all graphic devices (two right panels in RStudio).  Bring in necessary packages.

```{r}
rm(list = ls())
graphics.off()
library(ggplot2)
```

Check the working directory and change if needed.

```{r}
getwd()
```


TEMPERATURE PLOTS

Read in the temperature data .csv.

```{r}
AI_Temp <- read_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\Temperature Data\\AI_Temp_Logger_DateTime.csv")
```

Make a time series plot with the DO data and export to the Figures folder on GitHub.

```{r}
AI_Temp_Plot <- ggplot(AI_Temp, aes(x = Date_Time, y = Temp_C)) +
  geom_line() +
  xlab("Date and Time") +
  ylab("Temperature (\u00B0C)") +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(axis.title.y = element_text(margin = margin(r = 10)))

# ggsave("..\\..\\Figures\\Temperature Plots\\AI_Temp_Plot.png", width = 6, height = 4, units = "in")
```


DO PLOTS

Read in the DO data .csv.

```{r}
AA_DO <- read_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\DO Data\\AA_DO_Logger_DateTime.csv")
```

Make a time series plot with the DO data and export to the Figures folder on GitHub.

```{r}
AA_DO_Plot <- ggplot(AA_DO, aes(x = Date_Time, y = DO_mgL)) +
  geom_line() +
  xlab("Date and Time") +
  ylab("DO (mg/L)") +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(axis.title.y = element_text(margin = margin(r = 10)))

# ggsave("..\\..\\Figures\\DO Plots\\AA_DO_Plot.png", width = 6, height = 4, units = "in")
```

Repeat for all sites that had the DO logger rotation.

AAE (Utopia)

```{r}
AAE_DO <- read_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\DO Data\\AAE_DO_Logger_DateTime.csv")

AE_DO_Plot <- ggplot(AAE_DO, aes(x = Date_Time, y = DO_mgL)) +
  geom_line() +
  xlab("Date and Time") +
  ylab("DO (mg/L)") +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(axis.title.y = element_text(margin = margin(r = 10)))

# ggsave("..\\..\\Figures\\DO Plots\\AAE_DO_Plot.png", width = 6, height = 4, units = "in")
```

AC (HMSP Slough)

```{r}
AC_DO <- read_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\DO Data\\AC_DO_Logger_DateTime.csv")

AC_DO_Plot <- ggplot(AC_DO, aes(x = Date_Time, y = DO_mgL)) +
  geom_line() +
  xlab("Date and Time") +
  ylab("DO (mg/L)") +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(axis.title.y = element_text(margin = margin(r = 10)))

# ggsave("..\\..\\Figures\\DO Plots\\AC_DO_Plot.png", width = 6, height = 4, units = "in")
```

AH (Martin Slough)

```{r}
AH_DO <- read_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\DO Data\\AH_DO_Logger_DateTime.csv")

AH_DO_Plot <- ggplot(AH_DO, aes(x = Date_Time, y = DO_mgL)) +
  geom_line() +
  xlab("Date and Time") +
  ylab("DO (mg/L)") +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(axis.title.y = element_text(margin = margin(r = 10)))

# ggsave("..\\..\\Figures\\DO Plots\\AH_DO_Plot.png", width = 6, height = 4, units = "in")
```

AQ (Floral Lane Oxbow)

```{r}
AQ_DO <- read_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\DO Data\\AQ_DO_Logger_DateTime.csv")

AQ_DO_Plot <- ggplot(AQ_DO, aes(x = Date_Time, y = DO_mgL)) +
  geom_line() +
  xlab("Date and Time") +
  ylab("DO (mg/L)") +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(axis.title.y = element_text(margin = margin(r = 10)))

# ggsave("..\\..\\Figures\\DO Plots\\AQ_DO_Plot.png", width = 6, height = 4, units = "in")
```

P (Savage Slough)

```{r}
P_DO <- read_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\DO Data\\P_DO_Logger_DateTime.csv")

P_DO_Plot <- ggplot(P_DO, aes(x = Date_Time, y = DO_mgL)) +
  geom_line() +
  xlab("Date and Time") +
  ylab("DO (mg/L)") +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(axis.title.y = element_text(margin = margin(r = 10)))

# ggsave("..\\..\\Figures\\DO Plots\\P_DO_Plot.png", width = 6, height = 4, units = "in")
```

Site Z

```{r}
Z_DO <- read_csv("..\\..\\Data\\Derived Data\\DateTime Long Term Logger Data\\DO Data\\Z_DO_Logger_DateTime.csv")

Z_DO_Plot <- ggplot(Z_DO, aes(x = Date_Time, y = DO_mgL)) +
  geom_line() +
  xlab("Date and Time") +
  ylab("DO (mg/L)") +
  theme(axis.title.x = element_text(margin = margin(t = 10))) +
  theme(axis.title.y = element_text(margin = margin(r = 10)))

# ggsave("..\\..\\Figures\\DO Plots\\Z_DO_Plot.png", width = 6, height = 4, units = "in")
```

